Handwritten Digit Recognition Using Deep Convolutional Neural Network*

### 2022-04-28 paper/paper.tex
more minor fixes

\onecolumn
\maketitle
\begin{table}[!htp]
    \centering
    \begin{tabular}{ll}
        \textbf{Course Name:} & Special Topics in Computer Engineering\\
        \textbf{Course Instructor:} & Ahmed Bouridane\\
        \textbf{Module Number}: & 1502460
    \end{tabular}
\end{table}
\thispagestyle{plain}
\pagestyle{plain}
\begin{center}
    \textbf{Abstract}
\end{center}
    A Convolutional Neural Network (CNN) is a powerful tool for image classification.\@ However, despite existing since the late 1980s, they have been majorly dormant until the mid-2000s, which is when computing power and large databases of labeled data started becoming more accessible thanks to GPU technology and the internet, respectively.\@ This paper pits the use of a Deep Convolutional Neural Network (DCNN) against the MNIST database of handwritten digit images, and as will be seen by the end of the paper, the performance of these networks on a (cheap, consumer) GPU is simply a marvel of engineering, nearing human--level accuracy.
\footnotetext[1]{Code can be found at \href{https://github.com/ammar-elsabe/handwritten-digit-recognition-DCNN.git}{\texttt{github.com/ammar-elsabe/handwritten-digit-recognition-DCNN.git}}}

>>>>

\onecolumn
\maketitle
\begin{table}[!htp]
    \centering
    \begin{tabular}{ll}
        \textbf{Course Name:} & Special Topics in Computer Engineering\\
        \textbf{Course Instructor:} & Ahmed Bouridane\\
        \textbf{Module Number}: & 1502460
    \end{tabular}
\end{table}
\thispagestyle{plain}
\pagestyle{plain}
\begin{center}
    \textbf{Abstract}
\end{center}
    A Convolutional Neural Network (CNN) is a powerful tool for image classification.\@ However, despite existing since the late 1980s, they have been majorly dormant until the mid-2000s, which is when computing power and large databases of labeled data started becoming more accessible thanks to GPU technology and the internet, respectively.\@ This paper pits the use of a Deep Convolutional Neural Network (DCNN) against the MNIST database of handwritten digit images, and as will be seen by the end of the paper, the performance of these networks on a (cheap, consumer) GPU is simply a marvel of engineering, nearing human--level accuracy.
\footnotetext[1]{Code can be found at \href{https://github.com/ammar-elsabe/handwritten-digit-recognition-DCNN}{\texttt{github.com/ammar-elsabe/handwritten-digit-recognition-DCNN}}}
